---
title: "First own artistry"
author: "Sara"
date: "11/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r import, warning=FALSE, message=FALSE}
library(tidyverse)
library(viridis)
library(ggdark)
```
# get some random numbers
```{r random}
set.seed(1111)
n_points <- 1000
r1 <- sample(n_points) / (n_points * 2)
r2 <- sample(n_points) / n_points 
r3 <- sample(n_points) / (n_points * 0.5)
my_tib <- tibble(r1, r2, r3)
```

1000 random number each, scaled so that each is twice as big (maximally) as the previous vector
convert to long format
```{r}
my_tib <- my_tib %>%
  pivot_longer(cols = everything(),
               names_to = 'type',
               values_to = 'value')
```

add another random number for color
```{r}
color_values<- sample(n_points/20)
my_tib <- my_tib %>%
  mutate(color_values = rep_len(color_values, nrow(my_tib)))
```

and another one for size with fewer values
```{r}
size_values <- sample(n_points/100)
my_tib <- my_tib %>%
  mutate(size_values = rep_len(size_values, nrow(my_tib)))
```

scatter plot
```{r}
my_tib %>%
  ggplot(aes(x = value, y = type, color = color_values)) + 
  geom_jitter() + 
  scale_color_viridis(option = "mako") +
  coord_polar() +
  dark_theme_void() + 
  theme(legend.position = "none")
```

could do

+ try and use different color palettes per type
+ try a different function: somewhat random ellipse

```{r}
x <- sin(1:1000)
y <-tan(1:1000)
z <- tan(1:1000 - 500)
my_tib2 = tibble(x, y, z)
my_tib2 <- my_tib2 %>%
  mutate(color = rep_len(sample(20), nrow(my_tib2)))
```

```{r}
my_tib2 %>%
  ggplot(aes(x = x, y = y, color = x)) +
  geom_point() + 
  coord_polar() + 
  scale_color_viridis(option = "mako") +
  dark_theme_void() + 
  theme(legend.position = "none")

```

repeat this with different phase of tan and different radius and different colors...?
