---
title: "First rtistry"
author: "Sara"
date: "11/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Getting started with rtistry

for now I am entirely copying from and following this [blogpost](https://ivelasq.rbind.io/blog/rtistry-intro/)
```{r import, warning=FALSE, message=FALSE}
library(tidyverse)
library(viridis)
library(ggdark)
```

# Parametric equations
explained e.g. [here](https://lifethroughamathematicianseyes.wordpress.com/2014/11/13/parametric-equations/)

simplest parametric equation: combine sine and cosine to make circle
```{r}
circleFun <- function(center = c(0, 0), diameter = 1, npoints = 100){
    r = diameter / 2
    tt <- seq(0,2*pi,length.out = npoints)
    xx <- center[1] + r * cos(tt)
    yy <- center[2] + r * sin(tt)
    return(data.frame(x = xx, y = yy))
}
```

plot a circle
```{r}
dat <- 
  circleFun(c(1, -1), 2.3, npoints = 100)

ggplot(dat,aes(x, y)) +
  geom_path()
```

some parametric equation

```{r}
genFun <- function(center = c(0, 0), npoints = 500, c1 = 2.5, c2 = -5, c3 = 4.28, c4 = 2.3){
t <- seq(0, 2*pi, length.out = npoints)
xx <- center[1] + c1*(sin(c2*t)*sin(c2*t))*(2^cos(cos(c3*c4*t)))
yy <- center[2] + c1*sin(sin(c2*t))*(cos(c3*c4*t)*cos(c3*c4*t))
a <- data.frame(x = xx, y = yy)
    
return(a)
}
```

with few points evaluated
```{r}
dat <- 
  genFun(c(1,-1), npoints = 100)

ggplot(dat, aes(x, y)) +
  geom_path()
```

gets smoother with more points evaluated
```{r}
dat <- 
  genFun(c(1,-1), npoints = 500, c1 = 5, c2 = -3, c3 = 5, c4 = 2)

ggplot(dat, aes(x, y)) +
  geom_path()
```
## varying geoms

geom_line
```{r}
dat <- 
  genFun(c(1,-1), npoints = 5000)

ggplot(dat, aes(x, y)) +
  geom_line()
```

geom_point
```{r}
set.seed(1234)

dat <- 
  genFun(c(1,-1), npoints = 500)

dat %>% 
  ggplot(aes(x, y)) +
  geom_point()
```
## theme
use theme_void

## aesthetics

### size
```{r}
set.seed(1111)

dat <- 
  genFun(c(1,-1), npoints = 5000) %>% 
  mutate(rand_w = sample(n())/3000)

dat %>% 
  ggplot(aes(x, y)) +
  geom_point(size = dat$rand_w) +
  theme_void()
```

### shape
```{r}
dat %>% 
  ggplot(aes(x, y)) +
  geom_point(size = dat$rand_w,
             shape = 8) +
  theme_void()
```

### opacity
```{r}
set.seed(1234)

dat <- 
  dat %>% 
  mutate(rand_o = sample(n())/5000)

dat %>% 
  ggplot(aes(x, y)) +
  geom_point(size = dat$rand_w,
             alpha = dat$rand_o) +
  theme_void()
```

### color
combined with dark theme void
```{r}
set.seed(1234)

dat <- 
  dat %>% 
  mutate(rand_c = sample(n()))

dat %>% 
  ggplot(aes(x, y,  color = rand_c)) +
  geom_point(aes(size = rand_w,
             alpha = rand_o)) +
  scale_color_viridis(option = "magma") +
  coord_equal() +
  dark_theme_void() +
  theme(legend.position = "none")# remove legend
```

modify funcltion so that the random elements can be specified as parameters already
```{r}
genFun <- function(center = c(0, 0), npoints = 500, c1 = 2.5, c2 = -5, c3 = 4.28, c4 = 2.3, size_denom = 1, opacity_denom = 1, color_denom = 1){
    t <- seq(0, 2*pi, length.out = npoints)
    xx <- center[1] + c1*(sin(c2*t)*sin(c2*t))*(2^cos(cos(c3*c4*t)))
    yy <- center[2] + c1*sin(sin(c2*t))*(cos(c3*c4*t)*cos(c3*c4*t))
    rand_w <- sample(0:20, npoints, replace = TRUE)/size_denom
    rand_o <- sample(1:100, npoints, replace = TRUE)/opacity_denom
    rand_c <- sample(1:100, npoints, replace = TRUE)/color_denom
    a <- data.frame(x = xx, y = yy, rand_w = rand_w, rand_o = rand_o, rand_c = rand_c)
    
    return(a)
}
```

```{r}
set.seed(1111)

dat <- 
  genFun(c(0, 0), npoints = 5000, c1 = 5, c2 = -3, c3 = 4, c4 = 2, size_denom = 3, opacity_denom = 50)

dat %>% 
  ggplot(aes(x, y,  color = rand_c)) +
  geom_point(size = dat$rand_w,
             alpha = dat$rand_o) +
  scale_color_viridis(option = "mako") +
  dark_theme_void() +
  theme(legend.position = "none") # remove legend
```

```{r}
dat %>% 
  ggplot() +
  geom_point(aes(x, y,  color = rand_c),
             size = dat$rand_w,
             alpha = dat$rand_o) +
  geom_point(aes(-x, -y,  color = rand_c),
             size = dat$rand_w,
             alpha = dat$rand_o) +
  geom_point(aes(-y, x,  color = rand_c),
             size = dat$rand_w,
             alpha = dat$rand_o) +
  geom_point(aes(-y, -x,  color = rand_c),
             size = dat$rand_w,
             alpha = dat$rand_o) +
  scale_color_viridis(option = "magma") +
  dark_theme_void() +
  theme(legend.position = "none") # remove legend
```

could also check [this](https://github.com/Ijeamakaanyene/patterns/blob/main/zine/zine_radial_patterns.pdf) for inspiration
